---
title: "wine_report.Rmd"
output: html_document
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../"
    )
  })
---

install.packages("here")

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
i_am("individual-assignment-2-dinaa-kh.Rproj")
read.csv("Data/winequality-red.csv")

```
#DATA
```{r, include=FALSE}
#Used libaries
library(tidyverse)
library(ggplot2)
library(janitor)
library(tidyr)
library(here)
library(readr)
library(corrplot)

wineq <- read_csv ("~/Documents/misk-DSI/individual-assignment-2-dinaa-kh/Data/winequality-red.csv")

wineqc <- wineq %>%
  clean_names()

names(wineqc)[9] <- "ph"
```
This dataset is affiliated with red and white variants of the Portuguese "Vinho Verde" wine provided by UCIML.
variables provided from the dataset can be shown in this table:

| Variable             Description                                            
| ------------------------------------------------------------------------ 
Fixed acidity          acids involved with wine fixed or nonvolatile  
Volatile acidity      amount of acetic acid in wine, which at high levels can lead to an unpleasant taste               
Citric acid           citric acid  adds  freshness and flavor. 
Residual sugar        the amount of sugar left after fermentation
Chlorides             amount of salt in wine                         
Free sulfur dioxide   the free form of SO2                                   
Total sulfur dioxide  the amount of free and bound forms of S02                  
Density               depends on the percent of alcohol and sugar     
pH                    shows how acidic or basic a wine is                
Sulphate              additive contributes to S02 & acts as an antimicrobial 
Alcohol               percentage of alcohol by volume                        
Quality               a score between 0 and 10                               

#EDA
```{r}
#We took a look into our data using
str(wineqc)
summary(wineqc)
length(wineqc)
dim(wineqc)
names(wineqc)
summary(wineqc$quality)
table(wineqc$quality) 


```

```{r}
#For quality distirbution
ggplot(wineqc,aes(x=quality))+geom_bar(stat = "count",position = "dodge", fill = "light pink")+
  scale_x_continuous(breaks = seq(3,8,1))+
  ggtitle("Wine Quality Ratings distributed")+
  theme_classic()
```
we can see that majority of the quality is around 5-6. Around 82%

```{r}
#for the coralation
wine = cor(wineqc)
corrplot(wine)
#As the plot offers, alcohol has the most robust correlation with wine quality.
```
We checked how 11 features impacted the quality of wine using ggplot and boxplot

```{r}
#alcohol
ggplot(wineqc, aes(x = factor(quality), y =alcohol, fill = quality)) + 
  stat_boxplot(geom = "errorbar", width = 0.25) + 
  geom_boxplot() +
  guides(fill = guide_legend(title = "Quality"))+ xlab("quality")
```

```{r}
ggplot(wineqc, aes(quality, sulphates)) +
  geom_jitter(width = 0.55, alpha = 0.5, colour = "yellow") +
  geom_smooth(method=lm, se=FALSE, colour = "orange")
```
we can see how sulphate affects the quality

```{r}
wineqc%>%
  ggplot(aes(factor(quality), `fixed_acidity`, group=quality))+geom_boxplot()+ggtitle("Fixed Acidity/quality")+theme_classic()
#how fixed acidity has an affect on quality

```
how fixed acidity has an affect on quality


```{r}
ggplot(wineqc, aes(quality, citric_acid)) +
  geom_jitter(width = 0.55, alpha = 0.5, colour = "yellow") +
  geom_smooth(method=lm, se=FALSE, colour = "orange")
#the affect citric acid has on the quality.
```
the affect citric acid has on the quality.




## Conclusion
In conclusion wine quality is effected by 4 fetures : alcohol/sulphate/fixed acidity/citric acid
